
\section{Learning tasks}
\label{appendix:learning_tasks}

% cell((0..7, 0..6)).
% adjacent(right, (X+1,Y),(X,Y))   :- cell((X,Y)), cell((X+1,Y)).
% adjacent(left,(X,Y),  (X+1,Y)) :- cell((X,Y)), cell((X+1,Y)).
% adjacent(down, (X,Y+1),(X,Y))   :- cell((X,Y)), cell((X,Y+1)).

% adjacent(up,   (X,Y),  (X,Y+1)) :- cell((X,Y)), cell((X,Y+1)).

% \#modeh(state\_after(var(cell))).

% \#modeb(1, adjacent(const(action), var(cell), var(cell))).
% \#modeb(1, state\_before(var(cell)), (positive)).
% \#modeb(1, action(const(action)),(positive)).
% \#modeb(1, wall(var(cell))).

% \#max\_penalty(100).

% \#constant(action, right).
% \#constant(action, left).
% \#constant(action, down).
% \#constant(action, up).
% \#constant(action, non).

% \#pos({state\_after((1,4))}, {state\_after((2,4)),state\_after((1,5)),state\_after((0,4)),state\_after((1,3))}, {state\_before((1,4)). action(non). wall((1, 5)). wall((0, 4)). }).
% \#pos({state\_after((1,3))}, {state\_after((2,4)),state\_after((1,5)),state\_after((0,4)),state\_after((1,4))}, {state\_before((1,4)). action(up). wall((1, 5)). wall((0, 4)). }).
% \#pos({state\_after((1,3))}, {state\_after((2,3)),state\_after((1,4)),state\_after((0,3)),state\_after((1,2))}, {state\_before((1,3)). action(right). wall((2, 3)). wall((0, 3)). }).
% \#pos({state\_after((1,3))}, {state\_after((2,3)),state\_after((1,4)),state\_after((0,3)),state\_after((1,2))}, {state\_before((1,3)). action(right). wall((2, 3)). wall((0, 3)). }).
% \#pos({state\_after((1,3))}, {state\_after((2,3)),state\_after((1,4)),state\_after((0,3)),state\_after((1,2))}, {state\_before((1,3)). action(right). wall((2, 3)). wall((0, 3)). }).
% \#pos({state\_after((1,4))}, {state\_after((2,3)),state\_after((0,3)),state\_after((1,2)),state\_after((1,3))}, {state\_before((1,3)). action(down). wall((2, 3)). wall((0, 3)). }).
% \#pos({state\_after((2,4))}, {state\_after((1,5)),state\_after((0,4)),state\_after((1,3)),state\_after((1,4))}, {state\_before((1,4)). action(right). wall((1, 5)). wall((0, 4)). }).
% \#pos({state\_after((1,4))}, {state\_after((3,4)),state\_after((2,5)),state\_after((2,3)),state\_after((2,4))}, {state\_before((2,4)). action(left). wall((2, 5)). wall((2, 3)). }).



% \section{Abduction tasks}
\label{abduction}

% 1{action(down, T); action(up, T); action(right, T); action(left, T); action(non, T)}1 :- time(T), not finished(T).
% % \#show state_at/2.
% % \#show action/2.

% finished(T):- goal(T2), time(T), T >= T2.
% %  goal(T):- state_at((5, 1), T), not finished(T-1).
% goalMet:- goal(T).
% :- not goalMet.
% time(0..30).

% cell((0..6, 0..5)).
% % #minimize{1, X, T: action(X,T)}.
% adjacent(right, (X+1,Y),(X,Y))   :- cell((X,Y)), cell((X+1,Y)).
% adjacent(left,(X,Y),  (X+1,Y)) :- cell((X,Y)), cell((X+1,Y)).
% adjacent(down, (X,Y+1),(X,Y))   :- cell((X,Y)), cell((X,Y+1)).
% adjacent(up,   (X,Y),  (X,Y+1)) :- cell((X,Y)), cell((X,Y+1)).

% wall((1, 5)).
% wall((0, 4)).
% wall((2, 3)).
% wall((0, 3)).
% wall((2, 5)).
% wall((2, 2)).
% wall((0, 2)).
% wall((3, 5)).
% wall((4, 3)).
% wall((4, 2)).
% wall((2, 1)).
% wall((3, 0)).
% wall((4, 5)).
% wall((6, 4)).
% wall((5, 5)).
% wall((6, 3)).
% wall((5, 2)).
% wall((4, 0)).
% state_at((1, 4), 3).



\section{Ethics checklist}
\label{appendix:ethics_table}


{
\renewcommand*{\arraystretch}{1.3}
\begin{longtable}{ |p{13.2cm}|p{0.6cm}|p{0.6cm}| }
\hline
 & \bf Yes & \bf No \\
\hline

\multicolumn{3}{|l|}{\cellcolor{green!25}\bf Section 1: HUMAN EMBRYOS/FOETUSES} \\
\hline

Does your project involve Human Embryonic Stem Cells? & & \checkmark\\
\hline

Does your project involve the use of human embryos? & & \checkmark\\
\hline

Does your project involve the use of human foetal tissues / cells? & & \checkmark\\
\hline

\multicolumn{3}{|l|}{\cellcolor{green!25}\bf Section 2: HUMANS} \\
\hline

Does your project involve human participants? & & \checkmark\\
\hline

\multicolumn{3}{|l|}{\cellcolor{green!25}\bf Section 3: HUMAN CELLS / TISSUES} \\
\hline

Does your project involve human cells or tissues? (Other than from “Human Embryos/Foetuses” i.e. Section 1)? & & \checkmark\\
\hline

\multicolumn{3}{|l|}{\cellcolor{green!25}\bf Section 4: PROTECTION OF PERSONAL DATA} \\
\hline

Does your project involve personal data collection and/or processing? & & \checkmark\\
\hline

Does it involve the collection and/or processing of sensitive personal data (e.g. health, sexual lifestyle, ethnicity, political opinion, religious or philosophical conviction)? & & \checkmark\\
\hline

Does it involve processing of genetic information? & & \checkmark\\
\hline

Does it involve tracking or observation of participants? It should be noted that this issue is not limited to surveillance or localization data. It also applies to Wan data such as IP address, MACs, cookies etc. & & \checkmark\\
\hline

Does your project involve further processing of previously collected personal data (secondary use)? For example Does your project involve merging existing data sets? & & \checkmark\\
\hline

\multicolumn{3}{|l|}{\cellcolor{green!25}\bf Section 5: ANIMALS} \\
\hline

Does your project involve animals? & & \checkmark\\
\hline


\multicolumn{3}{|l|}{\cellcolor{green!25}\bf Section 6: DEVELOPING COUNTRIES} \\
\hline

Does your project involve developing countries? & & \checkmark\\
\hline

If your project involves low and/or lower-middle income countries, are any benefit-sharing actions planned? & & \checkmark\\
\hline

Could the situation in the country put the individuals taking part in the project at risk? & & \checkmark\\
\hline

\multicolumn{3}{|l|}{\cellcolor{green!25}\bf Section 7: ENVIRONMENTAL PROTECTION AND SAFETY} \\
\hline

Does your project involve the use of elements that may cause harm to the environment, animals or plants? & & \checkmark\\
\hline

Does your project deal with endangered fauna and/or flora /protected areas? & & \checkmark \\
\hline

Does your project involve the use of elements that may cause harm to humans, including project staff? & & \checkmark\\
\hline

Does your project involve other harmful materials or equipment, e.g. high-powered laser systems? & & \checkmark\\
\hline


\multicolumn{3}{|l|}{\cellcolor{green!25}\bf Section 8: DUAL USE} \\
\hline

Does your project have the potential for military applications? & & \checkmark\\
\hline

Does your project have an exclusive civilian application focus? & & \checkmark\\
\hline

Will your project use or produce goods or information that will require export licenses in accordance with legislation on dual use items? & & \checkmark\\
\hline

Does your project affect current standards in military ethics – e.g., global ban on weapons of mass destruction, issues of proportionality, discrimination of combatants and accountability in drone and autonomous robotics developments, incendiary or laser weapons? & & \checkmark\\
\hline

\multicolumn{3}{|l|}{\cellcolor{green!25}\bf Section 9: MISUSE} \\
\hline

Does your project have the potential for malevolent/criminal/terrorist abuse? & & \checkmark\\
\hline

Does your project involve information on/or the use of biological-, chemical-, nuclear/radiological-security sensitive materials and explosives, and means of their delivery? & & \checkmark\\
\hline

Does your project involve the development of technologies or the creation of information that could have severe negative impacts on human rights standards (e.g. privacy, stigmatization, discrimination), if misapplied? & \checkmark& \\
\hline

Does your project have the potential for terrorist or criminal abuse e.g. infrastructural vulnerability studies, cybersecurity related project? & & \checkmark\\
\hline

\multicolumn{3}{|l|}{\cellcolor{green!25}\bf Section 10: LEGAL ISSUES} \\
\hline

Will your project use or produce software for which there are copyright licensing implications? & \checkmark& \\
\hline

Will your project use or produce goods or information for which there are data protection, or other legal implications? & & \checkmark\\
\hline

\multicolumn{3}{|l|}{\cellcolor{green!25}\bf Section 11: OTHER ETHICS ISSUES} \\
\hline

Are there any other ethics issues that should be taken into consideration? & & \checkmark \\
\hline

\end{longtable}
}


